\section{Introduction}

If you are new to \LaTeX{}, I would suggest reading~\cite{Oetiker_2015}.  If you want to use Microsoft Word (or one of its many clones), you can download the official IEEE conference template from~\cite{Word_Template}.  The TA and tutors can provide \LaTeX{} support.  Use Word at your own risk.

The introduction is where you set the scene.  Here you reference other, related work, as well as a summary relating to how you improve upon said work~\cite{BibExample}.  In the sense of the practical reports, the introduction will summarise the experiment the practical is all about.

As a general rule of thumb, keep the introduction to the first column oe first page and don't put any \mbox{sub-sections} into it. But do so with care, obviously if you cannot set the scene and introduce the issue in such a limited space it is better to have a clearer rather than too short and unclear introduction.

Remember that, for bibliography citations to work, you have to include running Bib\TeX{} in the compile chain.  My TeXstudio~\cite{TeXstudio} compile chain for ``Build \& View'' is\linebreak
\vspace{-6mm}
\begin{verbatim}
txs:///bibtex | txs:///pdflatex |
txs:///bibtex | txs:///pdflatex |
txs:///view-pdf-internal
\end{verbatim}
% \linebreak stretches the line that is broken to the end of the column.  Use "\\" or "\newline" if you don't want it to do this.

General guide to an excellent introduction:

\begin{itemize}
	\item Put your work in context and set the scene appropriately (most important!). 
	\item Around 80-90\% of your references are typically cited in the introduction or introduction, background and literature review of your paper (engineering papers often don't have an explicit literature review section).
	\item The four key pieces of the introduction: 1) The subject/topic; 2) past work done in the area (related to your focus) and what is lacking; 3) The novelty/benefit of your contribution (i.e. preferably emphasising that it contributes new insights and knowledge); 4) The plan ahead for the remainder of the paper \footnote{a caveat to this: some authors and reviewers sometimes don't like the `plan ahead' which is usually just a paragraph, they may think it redundant and wasting space; that may be valid for a short paper but it often improves the readability and provides an effective bridge towards the rest of the paper.}.
\end{itemize}






\subsection{Drafting Markup}

When the template is in draft mode, you can use various helper macros, as illustrated below:

\old{This is old text that should be removed.}  \note{This is a note about something to remember, or comments from the proof-reader.}  \todo{This is something that still needs doing.}  When compiled with \verb|\Draftfalse|, the content of these macros are removed from the output, \rephrase{except something that needs to be rephrased.}

\note{You can also use cards, as follows:}

\todocard{
  This is a todo card.
  
  It is a minipage environment, so you can have all sorts of stuff in it.  It can be many paragraphs long, but don't make it too long, because \LaTeX\ will force the whole card onto a single page.

  \notecard{This is a nested note card.  You can nest cards of arbitrary types as deep as you like.}
}

